Open Science, Open Plant Pathology

### 2019-02-15 analysis/paper/paper.Rmd
Insert figure 1 in Word doc AND generate PDF

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles were not very open, failing to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---

@@

A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript. Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure 1).

A first level of reproducibility involves openly available research materials such as strains and/or nucleic acid sequences in public collections and citations for methods used. A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall. The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code. The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility \@ref(fig:workflow-dia).

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, results='hide', caption="An open and reproducible research workflow."}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

p <- export_svg(grViz(
  "
  digraph Fig1 {

  graph [fontsize = 8, nodesep=0.5]

  Question->Methodology->Data->Analysis
  Analysis->Manuscript
  Methodology->Description
  Methodology->Citation
  Methodology->Availability
  Manuscript->Supplement
  Data->'Data File'->'Public Repository'
  Analysis->'Binary Code'->Supplement
  Analysis->'Source Code'->'Public Repository'
  Data->'Binary File'->Supplement
  }
  ",
  width = 1000,
  height = 750
))

rsvg_pdf(charToRaw(p), "Figure 1.pdf")
```

@@

### Colophon

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

>>>>

---
title: "Open Science, Open Plant Pathology"
author:
  - Adam H. Sparks
  - Emerson Del Ponte
  - Sydney Everhart
  - Zachary Foster
  - Niklaus J Grünwald
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow. We randomly selected 200 articles published from 2012 to 2016 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles were not very open, failing to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 200 randomly selected articles from 2012 to 2016 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---

@@

A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript. Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices \@ref(fig:workflow-dia).

A first level of reproducibility involves openly available research materials such as strains and/or nucleic acid sequences in public collections and citations for methods used. A second level involves providing raw data and code as binary files (PDF or other non-text file) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall. The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following download of data and code. The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations. In the next section we present standards and tools that can be used to ensure reproducibility.

@@

# Figures

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An open and reproducible research workflow.', cache=FALSE, fig.env='figure'}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

p <- export_svg(
  grViz(
    "digraph Fig1 {
    graph [fontsize = 8, nodesep=0.5]

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_pdf(charToRaw(p), "Figure 1.pdf")

knitr::include_graphics("Figure 1.pdf")
```

# Colophon

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
sessionInfo()
```
